---
title: "Global Sustainable Energy Trends (2000–2020)"
subtitle: "commit or quit"
author:
  - Shakshi Shah
  - Annamalai Vikash Raam Manoj
  - Siyuan Yin
  - Xuanning Zhang
format:
  revealjs:
    theme: simple
    slide-number: true
    transition: fade
    incremental: false
    embed-resources: true
execute:
  echo: false
  warning: false
  message: false
---

## Problem Introduction {.smaller}

- Topic: renewable energy adoption and CO2 emissions
- Period: 2000–2020
- Countries: China, India, United States, Australia

::: fragment
**Research question:**  
How did renewable energy adoption and carbon emissions change across these major economies?
:::

---

## Dataset Description {.smaller}

- Source: Global Sustainable Energy dataset
- Coverage: 176 countries from 2000 to 2020
- Focus: four selected major economies
- Key variables:
  - Renewable energy share (%)
  - CO2 emissions (kt)

---

## Methodology {.smaller}

- Cleaned and prepared the dataset in R
- Standardised column names
- Filtered the four selected countries
- Selected renewable energy and CO2 emission variables
- Used 2019 for comparison due to missing 2020 observations
- Created trend and comparison visualisations using `ggplot2`
:::

```{r}
# CODE FRAMEWORK ONLY
# This section shows where the data preparation code should go.

# Load packages
# library(tidyverse)

# Load cleaned data
# energy_analysis <- read_csv("../Data/energy_analysis.csv")

# Check variable names
# names(energy_analysis)

# Filter selected countries if needed
# energy_analysis <- energy_analysis |>
#   filter(entity %in% c("China", "India", "United States", "Australia"))
```

---

## Results: CO2 Emissions Trend {.smaller}

```{r}
# CODE FRAMEWORK ONLY
# Replace CO2_EMISSIONS_VARIABLE with the correct CO2 emissions column name.

# ggplot(energy_analysis,
#        aes(x = year,
#            y = CO2_EMISSIONS_VARIABLE,
#            colour = entity)) +
#   geom_line() +
#   labs(
#     title = "CO2 Emissions Trends in Selected Economies",
#     x = "Year",
#     y = "CO2 Emissions (kt)",
#     colour = "Country"
#   ) +
#   theme_minimal()
```

- China had the highest CO2 emissions
- India’s emissions increased over time
- United States emissions declined overall
- Australia remained low and stable

---

## Results: Renewable Energy Trend {.smaller}

```{r}
# CODE FRAMEWORK ONLY
# Replace RENEWABLE_ENERGY_SHARE_VARIABLE with the correct renewable energy column name.

# ggplot(energy_analysis,
#        aes(x = year,
#            y = RENEWABLE_ENERGY_SHARE_VARIABLE,
#            colour = entity)) +
#   geom_line() +
#   labs(
#     title = "Renewable Energy Adoption Trends",
#     x = "Year",
#     y = "Renewable Energy Share (%)",
#     colour = "Country"
#   ) +
#   theme_minimal()
```

- India had the highest renewable energy share
- China declined first, then recovered slightly after 2012
- Australia and the United States increased slowly

---

## Results: 2019 Comparison {.smaller}

```{r}
# CODE FRAMEWORK ONLY
# This section should compare renewable energy share and CO2 emissions in 2019.

# energy_2019 <- energy_analysis |>
#   filter(year == 2019)

# ggplot(energy_2019,
#        aes(x = RENEWABLE_ENERGY_SHARE_VARIABLE,
#            y = CO2_EMISSIONS_VARIABLE,
#            label = entity)) +
#   geom_point() +
#   geom_text() +
#   labs(
#     title = "Renewable Energy Share and CO2 Emissions in 2019",
#     x = "Renewable Energy Share (%)",
#     y = "CO2 Emissions (kt)"
#   ) +
#   theme_minimal()
```

- India had the highest renewable energy share
- China had the highest CO2 emissions
- Renewable energy share alone did not explain emissions

---

## Discussion {.smaller}

- Renewable energy and CO2 emissions did not always move together
- Higher renewable share did not automatically mean lower emissions
- Emissions were also affected by:
  - population size
  - industrial activity
  - economic scale
  - energy demand
  - fossil fuel dependence


---

## Recommendations {.smaller}

- Continue investing in renewable energy infrastructure
- Improve grid infrastructure and energy storage
- Combine renewable energy policies with low-carbon policies
- Focus on high-emission sectors:
  - power generation
  - transport
  - heavy industry


---

## Conclusion {.smaller}

- Renewable energy adoption is important
- But it does not explain emissions by itself
- Each country has a different energy and economic context
- A complete analysis should consider renewable energy, fossil fuel use, energy demand, and national differences